\documentclass{article}
\usepackage{geometry}
\title{Grading system of project assignments}
\author{Mikael B. Kiste}

\begin{document}
	\maketitle
	%\tableofcontents
		\begin{itemize}
	\item{\textbf{5p Abstract} accurate and informative?}
	\item{\textbf{10p Introduction} status of problem and the major objectives}
	\item{\textbf{20p Formalism/methods} Discussion of the methods used and their basis/suitability}
	\item{\textbf{20p Code/Implementations/test} Readability of code, implementation, testing and discussion of benchmarks}
	\item{\textbf{20p Analysis} of results and the effectiveness of their selection and presentation. Are the results well understood and discussed?}
	\item{\textbf{10p Conclusions, discussions and critical comments} on what was learned about the method used and on the results obtained. Possible directions and future improvements?}
	\item{\textbf{10p Clarity} Clarity of figures and overall presentation. Too much or too little?}
	\item{\textbf{5p eferencing} relevant works cited accurately?}
	\end{itemize}

	\newpage
	\section*{5p Abstract}
	Accurate and informative?
	\section*{10p Introduction}
	Status of problem and the major objectives
	\section*{20 Formalism/methods}
	Discussion of the methods used and their basis/suitability
	\section*{20 Code/Implementations/test}
	Readability of code, implementation, testing and discussion of benchmarks
	\section*{20 Analysis}
	Analysis of results and the effectiveness of their selection and presentation. Are the results well understood and discussed?
	\section*{10 Conclusions, discussions and critical comments}
	on what was learned about the method used and on the results obtained. Possible directions and future improvements?
	\section*{10 Clarity}
	Clarity of figures and overall presentation. Too much or too little?
	\section*{5 Referencing}
	Relevant works cited accurately?
	
	\newpage
	\section*{tabulated}
	\begin{tabular}{l l}
		5	&	Abstract: accurate and informative?\\
		10	&	Introduction: status of problem and the major objectives\\
		20	&	Formalism/methods: Discussion of the methods used and their basis/suitability\\
		20	&	Code/Implementations/test: Readability of code, implementation, testing and discussion of benchmarks\\
		20	&	Analysis: of results and the effectiveness of their selection and presentation. Are the results well understood and discussed?\\
		10	&	Conclusions, discussions and critical comments: on what was learned about the method used and on the results obtained. Possible directions and future improvements?\\
		10	&	Clarity of figures and overall presentation. Too much or too little?\\
		5	&	Referencing: relevant works cited accurately?
	\end{tabular}
\end{document}